Twisted \(M\)-theory and its perturbative quantization.

### 2021-03-29 modules.tex
modules update

\def\pv{{\rm PV}}
\def\PV{{\rm PV}}
\def\T{{\rm T}}
\def\del{\partial}
\def\Vect{{\rm Vect}}

@@

\subsection{$n=2$} 
Consider the case $\dim_{\CC}(X) = 5$. 
Introduce the new brackets
\begin{align*}
[\gamma_1, \gamma_2]_2 &= (\partial \gamma_1 \partial \gamma_2)\vee \Omega \in \PV^1(X) \\
[\gamma_1, \gamma_2, \gamma_3]_3 & = (\gamma_1 \partial \gamma_2 \partial \gamma_2)\vee \Omega \in \Omega^0(X) \\
[\gamma_1, \gamma_2, \nu]_3 & = \nu (\partial \gamma_1 \partial \gamma_2)\vee \Omega \in \PV^1(X) .
\end{align*}

@@

>>>>

\def\pv{{\rm PV}}
\def\PV{{\rm PV}}
\def\T{{\rm T}}
\def\del{\partial}
\def\Vect{{\rm Vect}}
\def\div{\partial_\Omega}

@@

\subsection{$n=2$} 
Consider the case $\dim_{\CC}(X) = 5$. 
Introduce the new brackets
\begin{align*}
[\gamma_1, \gamma_2]_2 &= (\partial \gamma_1 \partial \gamma_2)\vee \Omega \in \PV^1(X) \\
[\gamma_1, \gamma_2, \gamma_3]_3 & = (\gamma_1 \partial \gamma_2 \partial \gamma_3)\vee \Omega \in \Omega^0(X) \\
[\gamma_1, \gamma_2, \nu]_3 & = \nu (\partial \gamma_1 \partial \gamma_2)\vee \Omega \in \PV^1(X) .
\end{align*}

@@

\section{Type IIA}

Let $X$ be a Calabi--Yau manifold of dimension four. 
Consider the following $\ZZ/2$-graded cochain complex
\[
\begin{tikzcd}
\ul{even} & \ul{odd} \\
& \PV^0(X)_\eta \\
\PV^1(X)_\mu \ar[r, "\partial_\Omega"] & \PV^0 (X)_\nu \\
\PV^4(X)_\beta \ar[r, "\partial_\Omega"] & \PV^3(X)_\gamma \\
\PV^4(X)_\theta
\end{tikzcd}
\]

There is a $\ZZ/2$-graded dg Lie algebra structure on this complex defined by the nontrivial brackets
\begin{align*}
[\eta, \theta] & = \{\eta, \theta\} \in \PV^3_\gamma \\
[\nu, \beta] & = \{\nu, \beta\} \in \PV^3_\gamma \\ 
[\mu, \Phi] & = \{\mu, \Phi\} \in \PV^k_\Phi
\end{align*}
where in the last equation $\Phi$ stands for any polyvector field of type $k$ in the complex.

\begin{prop}
The formulas 
\begin{align*}
[\gamma, \gamma'] & = (\partial_\Omega \gamma) (\partial_\Omega \gamma') \in \PV^4_\theta \\
[\eta, \gamma] & = \{\eta, \div \gamma\} \in \PV^1_\mu \\
%[\gamma, \theta] & = 0 \in \PV^4_\theta ?? \\
[\eta, \gamma, \gamma']_3 & = \frac12 \left(\{\{\eta, \gamma\}, \gamma'\} + symm\right) \in \PV^4_\beta \\
[\nu, \gamma, \gamma']_3 & = \frac12 \left(\{\{\nu, \gamma\}, \gamma'\} + \cdots \right) \in \PV^4_\theta
\end{align*}
\end{prop}
define an $L_\infty$ deformation of the dg Lie algebra. 
\begin{proof}
First, we observe that the new $2$-ary bracket is trivially compatible with the differential. 
Next, we check the $3$-ary $L_\infty$ relations involving the new $2,3$-ary brackets. 
The only nontrivial $3$-ary relations to check are
\begin{itemize}
\item[(1)] $\div [\eta, \gamma, \gamma']_3 = \{\eta, [\gamma, \gamma']\} + \{[\eta, \gamma], \gamma'\} + \{[\eta, \gamma'], \gamma\}.$
\item[(2)] $- [\div \mu, \gamma, \gamma']_3  = \{\mu, [\gamma, \gamma']\} + \{\{\mu, \gamma\}, \gamma'\} + \{\{\mu, \gamma'\}, \gamma\}$.

\end{itemize}

Substituting the definitions of the $2$-ary Lie brackets, we see that (1) follows from the following lemma. 
\begin{lem}
For all $\eta, \gamma, \gamma'$ one has
\begin{equation}\label{eqn:C43ary}
\div \{\{\eta, \gamma\}, \gamma'\} = \{\eta, \div \gamma \div \gamma'\} + \{\{\eta, \div \gamma\}, \gamma'\} + \{\{\eta, \div \gamma'\}, \gamma\} .
\end{equation}
\end{lem}
\begin{proof}
This is a direct calculation. 
Consider the last two terms on the right hand side:
\[
\{\{\eta, \div \gamma\}, \gamma'\} + \{\{\eta, \div \gamma'\}, \gamma\} .
\]
Since $\div$ is a derivation for $\{\cdot,\cdot\}$ we can rewrite this expression as
\[
\{\div\{\eta, \gamma\}, \gamma'\} + \{\{\eta, \div \gamma'\}, \gamma\} = \div \{\{\eta, \gamma\}, \gamma'\} - \{\{\eta, \gamma\}, \div \gamma'\} + \{\{\eta, \div \gamma'\}, \gamma\} .
\]
By the Jacobi identity for $\{\cdot, \cdot\}$ this expression is equal to
\[
\div\{\{\eta, \gamma\}, \gamma'\} - \{\{\gamma, \div \gamma'\}, \eta\} 
\]
The lemma reduces to the following BV relation:
\[
\{\eta, \div \gamma \div \gamma'\} = \{\eta, \{\gamma, \div \gamma'\}\} .
\]

%By the BV relation, the left hand side is 
%\[
% \{\eta, \div(\gamma \div \gamma')\} = \{\eta, \{\gamma, \div \gamma'\}\} + \{\eta, (\div\gamma) (\div \gamma')\}.
% \]
\end{proof}

Finally, there are the following $4$-ary $L_\infty$ relations to check. 
\begin{itemize}
\item[(1)] $\{\nu, [\eta, \gamma, \gamma']_3\} + \{\eta, [\nu, \gamma, \gamma']_3\} = 0.$ 
\item[(2)]
\end{itemize}

\brian{Maybe we need to symmetrize to use $[\eta, \gamma, \gamma']_3 = \{\eta, \{\gamma, \gamma'\}\}$.}
\end{proof}
